% Resume 2.0 (2009-04-12)
% Copyright 2009 Zach Scrivena
% zachscrivena@gmail.com
% http://zs.freeshell.org/latexresume/
%
% This document is released under the
% Creative Commons Attribution 3.0 Unported License
% http://creativecommons.org/licenses/by/3.0/

%%%%%%%%%%%%%%
%% PREAMBLE %%
%%%%%%%%%%%%%%

\documentclass[letterpaper,10pt,oneside]{article}
%\documentclass[a4paper,10pt,oneside]{article}
\usepackage[OT1]{fontenc}
\usepackage{enumitem}
\usepackage{ifthen}
\usepackage{longtable}
\usepackage{setspace}
\usepackage[left=.8in,right=.8in,top=.6in,bottom=0.6in,nohead,nofoot]{geometry}
\usepackage{marvosym}
\usepackage{times}
\usepackage{url}

\usepackage[bookmarks,
pdftitle={Resume},
pdfauthor={Mihir Shete},
pdfsubject={},
pdfcreator={},
pdfproducer={},
pdfkeywords={},
pdfpagemode={},
pdfstartview=FitH,
colorlinks=true,
linkcolor=black,   %Color for normal internal links.
anchorcolor=black, %Color for anchor text.
citecolor=green,   %Color for bibliographical citations in text.
filecolor=magenta, %Color for URLs which open local files.
menucolor=red,     %Color for Acrobat menu items.
urlcolor=black]{hyperref}

\newcommand{\longmonth}[1]{%
\ifthenelse{\equal{#1}{1}}{January}{}%
\ifthenelse{\equal{#1}{2}}{February}{}%
\ifthenelse{\equal{#1}{3}}{March}{}%
\ifthenelse{\equal{#1}{4}}{April}{}%
\ifthenelse{\equal{#1}{5}}{May}{}%
\ifthenelse{\equal{#1}{6}}{June}{}%
\ifthenelse{\equal{#1}{7}}{July}{}%
\ifthenelse{\equal{#1}{8}}{August}{}%
\ifthenelse{\equal{#1}{9}}{September}{}%
\ifthenelse{\equal{#1}{01}}{January}{}%
\ifthenelse{\equal{#1}{02}}{February}{}%
\ifthenelse{\equal{#1}{03}}{March}{}%
\ifthenelse{\equal{#1}{04}}{April}{}%
\ifthenelse{\equal{#1}{05}}{May}{}%
\ifthenelse{\equal{#1}{06}}{June}{}%
\ifthenelse{\equal{#1}{07}}{July}{}%
\ifthenelse{\equal{#1}{08}}{August}{}%
\ifthenelse{\equal{#1}{09}}{September}{}%
\ifthenelse{\equal{#1}{10}}{October}{}%
\ifthenelse{\equal{#1}{11}}{November}{}%
\ifthenelse{\equal{#1}{12}}{December}{}}

\newcommand{\shortmonth}[1]{%
\ifthenelse{\equal{#1}{1}}{Jan}{}%
\ifthenelse{\equal{#1}{2}}{Feb}{}%
\ifthenelse{\equal{#1}{3}}{Mar}{}%
\ifthenelse{\equal{#1}{4}}{Apr}{}%
\ifthenelse{\equal{#1}{5}}{May}{}%
\ifthenelse{\equal{#1}{6}}{Jun}{}%
\ifthenelse{\equal{#1}{7}}{Jul}{}%
\ifthenelse{\equal{#1}{8}}{Aug}{}%
\ifthenelse{\equal{#1}{9}}{Sep}{}%
\ifthenelse{\equal{#1}{01}}{Jan}{}%
\ifthenelse{\equal{#1}{02}}{Feb}{}%
\ifthenelse{\equal{#1}{03}}{Mar}{}%
\ifthenelse{\equal{#1}{04}}{Apr}{}%
\ifthenelse{\equal{#1}{05}}{May}{}%
\ifthenelse{\equal{#1}{06}}{Jun}{}%
\ifthenelse{\equal{#1}{07}}{Jul}{}%
\ifthenelse{\equal{#1}{08}}{Aug}{}%
\ifthenelse{\equal{#1}{09}}{Sep}{}%
\ifthenelse{\equal{#1}{10}}{Oct}{}%
\ifthenelse{\equal{#1}{11}}{Nov}{}%
\ifthenelse{\equal{#1}{12}}{Dec}{}}

% Style settings
\pagestyle{empty}
\setlength{\parindent}{0in}
\renewcommand{\thefootnote}{\fnsymbol{footnote}} % change footnote symbols

% Macros
\newenvironment{myresume}[2]{\pdfbookmark{#1}{#1}{\LARGE{#1}}\vspace{1mm}\hrule\vspace{-3mm}\begin{longtable}{p{0.12\textwidth} p{0.83\textwidth}}~&#2}{\end{longtable}}
\renewcommand{\section}[2]{\vspace{-1.3em}\\\pdfbookmark{#1}{#2}{\singlespace\textsc{#1}}&}
\newcommand{\firstentry}[1]{\newline#1}
\newcommand{\entry}[1]{\vspace{-0.8em}\\~&#1}
\newcommand{\hide}[1]{}

% Datestamp format: \datestamp{YEAR}{MONTH}{DAY}
%\newcommand{\datestamp}[3]{\longmonth{#2} #3, #1}
%\newcommand{\datestamp}[3]{\shortmonth{#2} #3, #1}
\newcommand{\datestamp}[3]{\shortmonth{#2} #1}

%%%%%%%%%%%%%%%%
%% NAME BLOCK %%
%%%%%%%%%%%%%%%%

\begin{document}
\begin{myresume}{Mihir Shete}{\small
Department of Computer Sciences       \hfill +1-608-960-5708 \Mobilefone \newline
University of Wisconsin-Madison       \hfill \href{mailto:smihir@cs.wisc.edu}{\textit{smihir@cs.wisc.edu}} \Letter \newline
Madison, WI 53706                     \hfill \href{https://pages.cs.wisc.edu/~smihir}{\textit{homepage}} \ComputerMouse \newline   
}

%%%%%%%%%%%%%%%
%% EDUCATION %%
%%%%%%%%%%%%%%%

\section{Education}{education}
\firstentry{
    \href{http://www.cs.wisc.edu/}{\textbf{University of Wisconsin-Madison}} \hfill \small{\datestamp{2015}{09}{15} -- \datestamp{2017}{05}{14}} \newline
    MS in Computer Science \newline
    {\small \textbf{Coursework}: Advanced Operating Systems, Introduction to Computer Networks, Distributed Systems, Big Data Systems, Machine Learning.}
}

\entry{
    \href{http://www.bits-goa.ac.in/}{\textbf{Birla Institute of Technology and Science - Pilani, Goa Campus}} \hfill \small{\datestamp{2006}{08}{15} -- \datestamp{2010}{05}{15}} \newline
    B.E.(Hons.) in Electronics And Instrumentation \newline
    {\small Concentrated on projects and internships in the areas of Embedded systems' design and development.}
}

%%%%%%%%%%%%%%%%%%%%%%%%%
%% WORK EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}{experience}
\firstentry{
    {\textbf{Apple}} \hfill {\small Cupertino, CA} \newline
    Software Engineer \hfill \small{\datestamp{2017}{07}{03} -- Present}
    \begin{itemize}[noitemsep,nolistsep]
        \item \small {Working on Always on Processor(AOP) for Apple's devices}
    \end{itemize}
}

\entry{
    {\textbf{ZeroStack}} \hfill {\small Mountain View, CA} \newline
    Member of Technical Staff, Intern \hfill \small{\datestamp{2016}{05}{15} -- \datestamp{2016}{08}{02}}
    \begin{itemize}[noitemsep,nolistsep]
        \item \small {Evaluated OpenStack Cinder's Image-Volume cache for speeding up volume creation.}
        \item \small {Developed a framework to run ZeroStack environment on OpenStack to test scalability of the solution.}
    \end{itemize}
}

\entry{
    {\textbf{Qualcomm}} \hfill {\small Hyderabad, India} \newline
    Senior Software Engineer \hfill \small{\datestamp{2012}{07}{15} -- \datestamp{2015}{07}{11}}
    \begin{itemize}[noitemsep,nolistsep]
        \item \small {Maintainer of 802.11 driver's data path and the DMA driver for Linux.}
        \item \small {Worked on optimizing the data path and the Linux scheduler for Heterogenous Multiprocessors.}
        \item \small {Contributed in the development process of a data offload engine between 802.11 and LTE processors.}
    \end{itemize}
}

\entry{
    {\textbf{TeamF1 Networks}} \hfill {\small Hyderabad, India} \newline
    Software Engineer \hfill \small{\datestamp{2010}{05}{31} -- \datestamp{2012}{06}{23}}
    \begin{itemize}[noitemsep,nolistsep]
        \item \small {Design and Development of Linux device drivers for 802.11 Wireless SoCs in Enterprise Routers.}
    \end{itemize}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACADEMIC PROJECTS AND RESEARCH %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Academic Projects \&\newline Research}{projects}
\firstentry{
    {\textbf{Make Copy-on-Write Great Again}} \newline
    University of Wisconsin-Madison \small{\hfill \datestamp{2016}{01}{23} -- \datestamp{2017}{05}{14}} \newline
    Prof. Mike Swift \newline
    We are working on rethinking copy-on-write mechanisms and policies to reduce overhead of handling copy-on-write
    faults on large pages. These generic techniques can also be applied in the areas of File Systems where copy-on-write
    mechanisms are used for creating snapshots. We showcased our work in \textit{Redis Conference 2016} held in San Fransisco.
}
\vspace{10pt}
\entry{
    {\textbf{Geo-Distributed Machine Learning}} \newline
    University of Wisconsin-Madison \small{\hfill \datestamp{2016}{09}{23} --  \datestamp{2016}{12}{1}} \newline
	Prof. Aditya Akella \newline
    Multinational organizations have data spread across geographically distributed datacenters. Running traditional 
    machine learning algorithms on the geo-distributed data can be costly in terms of time required for convergence
    and money spent to transfer data to a centralized datacenter. We are looking into a hierarchical parameter server
    based model to address these issues.

}
\vspace{10pt}
\entry{
    {\textbf{Stressing The HDFS Maintenance System}} \newline
    University of Wisconsin-Madison \small{\hfill \datestamp{2016}{09}{23} --  \datestamp{2016}{12}{23}} \newline
	Prof. Remzi Arpaci-Dusseau \newline
    Developed a framework to run Hadoop in containers so that we can test large scale HDFS cluster on limited hardware
    resources. We then used this framework to stress the HDFS mainenance system and devised a simple formula to predict
    the probability of data loss depending on the rate of node failures. We also proposed alternative mehcanisms and policies
    to prevent the maintenance system from hampering the normal day-to-day Hadoop operations.
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% OPEN SOURCE CONTRIBUTIONS %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Open Source}{contributions}
    \begin{itemize}[noitemsep,nolistsep,leftmargin=*,label={},topsep=0pt]
        \item \small {\textbf{MSM Linux Kernel}: Subsystem-Restart feature development and wireless regulatory framework maintenance}
        \item \small {\textbf{Prima Driver}: Added code to support new DMA hardware and worked on data path maintenance}
        \item \small {\textbf{HTCondor}: Contributing on developing an improved unit-test framework in perl and C}
    \end{itemize}

%%%%%%%%%%%%
%% SKILLS %%
%%%%%%%%%%%%
\section{Technical Skills}{skills}
    \begin{itemize}[noitemsep,nolistsep,leftmargin=*,label={},topsep=0pt]
        \item \small {\textbf{Programming}: C, Go, Python, C++, Perl, Lua, Shell Scripting, Javascript, Latex, Matlab, Java}
        \item \small {\textbf{Tools}: Vim, Gdb, SystemTap, Eclipse, Android Development Studio}
    \end{itemize}
\end{myresume}
\end{document}
