\cvsection{Experience}
\begin{cventries}
  \cventry
    {Senior Engineer}
    {Qualcomm}
    {Hyderabad, India}
    {July 2012 - July 2015}
    {
      \begin{cvitems}
        \item{As a member of Wireless Connectivity group was involved in 
              design and development of firmware and Linux device drivers 
              for Qualcomm's wireless chipsets.}
        \item{Primarily contributed to Qualcomm's opensource \textbf{Prima}
              driver and was the maintainer of data path and the DMA driver.}
        \item{Collaborated with the Linux community to engineer the regulatory 
              framework in Prima driver.}
      \end{cvitems}
    }

  \cventry
    {Software Engineer}
    {TeamF1 Networks}
    {Hyderabad, India}
    {May 2010 - June 2012}
    {
      \begin{cvitems}
        \item{Design and Development of Linux device drivers for 802.11 Wireless SoCs 
              in Enterprise Routers.}
        \item{Worked on securing the WiFi Alliance's 802.11n certification for 
              interoperability.}
        \item{Involved in development of a 802.11r solution independent of the available 
              open source alternatives.}
        \item{Implemented the RSTP functionality for Access Points.}
      \end{cvitems}
    }

  \cventry
    {Student Intern}
    {HTCondor}
    {Madison, Wisconsin}
    {September 2015 - PRESENT}
    {
      \begin{cvitems}
        \item{Design and development of regression test framework for HTCondor, which 
              is an Open-Source software for coarse-grained distributed parallelization 
              of computationally intensive tasks.}
      \end{cvitems}
    }

  \cventry
    {Professional Assistant}
    {Birla Institute of Technology and Science - Pilani, Goa Campus}
    {Goa, India}
    {January 2010 - May 2010}
    {
      \begin{cvitems}
        \item{Professional Assistant for the course - 
              Analog Electronics(INSTR C364)}
        \item{Responsibilities included overseeing and grading Lab sessions.}
        \item{Involved in designing assignments for the students.}
      \end{cvitems}
    }

  \cventry
    {Co-Op}
    {Cypress Semiconductor}
    {Chennai, India}
    {July 2009 - December 2009}
    {
      \begin{cvitems}
        \item{Designed a Blood Pressure Monitor reference solution using Cypress' SoCs.}
        \item{Involved in PCB design and development.}
        \item{Developed BP calculating algorithms based on the current research and implemented them in C and Matlab.}
      \end{cvitems}
    }

\end{cventries}
