\cvsection{Academic Projects \& Research}
\begin{cventries}
  \cventry
    {Internet of Things Laboratory, UW - Madison}
    {Smart Shoes in Healthcare Management}
    {Madison, Wisconsin}
    {October 2015 - PRESENT}
    {
      \begin{cvitems}
      \item{Our Aim is to build a continuous gait monitoring device which can be used in the healthcare
          industry for managing recovery of patients recovering after hip and knee surgeries.} 
      \item{Our first demonstration won the \textbf{Most Innovative Technlogy} award in the IoT Open-House at UW - Madison.}
      \item{We are currently working on developing robust algorithms and optimizing our system for efficiency and accuracy.}
      \end{cvitems}
    }
  \cventry
    {BITS - Pilani, Goa Campus}
    {Design and Development of Blood Pressure Monitor}
    {Goa, India}
    {Jan. 2010 - April 2010}
    {
      \begin{cvitems}
        \item{Developed simulation of circuits and filters involved in the designing of a BP Monitor so that they can be improved upon.}
        \item{Another aspect of this project was to survey available BP calculating algorithms and implement them in Matlab/Octave so that 
              they can be studied in detail and be improved for better accuracy.}
      \end{cvitems}
    }
  \cventry
    {BITS - Pilani, Goa Campus}
    {Design and Verification of Safety Critical Systems}
    {Goa, India}
    {Jan. 2010 - April 2010}
    {
      \begin{cvitems}
      \item{A survey of the established standards for designing safety critical systems guided by 
            \textbf{\href{http://universe.bits-pilani.ac.in/goa/anupkr/profile}{Dr. K.R Anupama}}.}
      \end{cvitems}
    }
\end{cventries}
